Model of Models' stuff

### 2023-05-22 minos/testing/model_of_models_work.Rmd
Started to functionalise plotting coefficients. Have function for reading in models and extracting coefficients to a dataframe, now need function for visualising each predictor group separately (or altogether)

@@

>>>>

```{r}
mod.list <- list.files(mod.path, pattern = '.+.rds', full.names = TRUE)

mod.models <- lapply(mod.list, FUN=readRDS)

mod.coefs <- as.data.frame(sapply(mod.models, function(x) return(coefficients(x))))

mod.coefs <- tibble::rownames_to_column(mod.coefs, 'predictor')
```

@@

# Function

```{r}

## Function to collect coefficients from a set of models into a dataframe
collect_coefficients_to_df <- function(trans.path, var, mod.type) {

  #TODO: find a way to write these as os agnostic paths instead of just pasting
  # https://stackoverflow.com/questions/8197027/raw-text-strings-for-file-paths-in-r
  mod.path <- paste0(trans.path, '/', var, '/', mod.type, '/')
  # list all rds files in dir
  file.list <- list.files(mod.path, pattern = ".+.rds", full.names = TRUE)
  # read all .rds models into a list
  mod.list <- lapply(mod.list, FUN=readRDS)
  # Now collect all coefficients into a dataframe, each column is 1 year
  mod.coefs <- sapply(mod.list, function(x) return(coefficients(x)))

  return(mod.coefs)
}

```
